\documentclass[margin]{res}

\PassOptionsToPackage{svgnames}{xcolor}
\usepackage[object=vectorian]{pgfornament}
\usepackage{lipsum, tikz, url, tabularx}

\topmargin = -0.75in
\addtolength{\oddsidemargin}{-.10in}
\setlength{\textheight}{11in} % increase text height to fit resume on 1 page

%% tex.stackexchange.com/questions/32711/totally-sweet-horizontal-rules-in-latex
\newcommand{\sweetline}[1]{
	\setlength{\parskip}{1.5ex}
	\nointerlineskip
	\hspace{\fill}
	\resizebox{0.33\linewidth}{1.25ex}
	{
    	\begin{tikzpicture}
			\node (C) at (0,0) {};
			\node (D) at (9,0) {};
			\path (C) to [ornament=#1] (D);
		\end{tikzpicture}
	}
	\hspace{\fill}
	\par
	\nointerlineskip
}

\newcommand{\Sharp}{\nolinebreak\hspace{-.05em}\raisebox{.6ex}{\scriptsize\bf \#}}
\usepackage{enumitem}

\newcommand{\sex}[1]{\section{\fontsize{13}{13}\selectfont{#1}}}

\newcommand{\tit}[1]{{
	\fontsize{11}{12}
	\selectfont
	\textbf{#1}
}}

\newcommand{\vs}[0]{\vspace{2px}}

\newenvironment{noindlist}
	{\begin{list}{}{
		\labelsep=0em \labelwidth=0em \leftmargin=0em \itemindent=0em
		\itemsep=3pt
	}}
	{\end{list}}

\begin{document}

{\centering
	\huge{Andy Hanson} \normalsize \\
	(703) 402-2284 \quad \url{andy.pj.hanson@gmail.com} \\
	\textbf{Please prefer} \url{andy-hanson.me/resume} \\
}


\begin{resume}

%\sweetline{82}

\sex{skill}
\begin{tabularx}{\textwidth}{ | l X }
	\emph{proficient in} & javascript (typescript, coffeescript, babel), c\Sharp, python \vs \\
	\emph{familiar with} & java (scala), ruby, c++, c, glsl, html (jade), css (stylus) \vs \\
	\emph{tools} & git, github, gulp, require.js, browserify, npm, bower \vs \\
	\emph{practices} & testing, linting, documenting, small \& pure funtions, refactoring, modularity
\end{tabularx}

\sex{work}
	\tit{FaunaDB}, San Francisco, CA \enspace \emph{Associate Software Engineer} \hfill \textsf{Jun 2015-Jan 2016} \\
	Worked on clients for a new database for python, ruby, javascript, and c\Sharp. \\
	Clients include REST client, error handling, (de)serialization, query language, and ORM, with tests and documentation.
	C\Sharp and javascript clients are asynchronous. \\
	Worked on the website, a rails application built with FaunaDB. Work was mostly server-side.
	
	\tit{IntentSoft}, Bellevue, WA \enspace \emph{Software Analyst and Developer} \hfill \textsf{Jul 2014-Mar 2015} \\
	Worked on a layout system. System takes as input a tree of content nodes (analogous to DOM nodes) and outputs a tree of graphical nodes (which have exact locations). \\
	Rewrote part of system that queried content locations to be closer to purely functional.
	Wrote tests, discovered and fixed bugs, and participated in design and implementation of new features.

\sex{school}
	\tit{Rensselaer Polytechnic Institute}, Troy, NY \hfill \textsf{GPA 3.94/4.0 \quad 2012-2014} \\
	Pending Bachelor of Science in Computer Science.

	\tit{Digipen Institute of Technology}, Redmond, WA \hfill \textsf{GPA 3.49/4.0 \quad 2011-2012} \\
	Made one game in ProjectFUN on a team of 3. \\
	Responsible for program, sound, and some graphics.

\sex{code}
	\begin{noindlist}
	\item \tit{mason} \enspace \small{programming language} \hfill \textsf{2014-} \\
	New language compiling to javascript. Several projects have been written in it already.
	
	\item \tit{esast} \enspace \small{javascript AST} \hfill \textsf{2015-} \\
	Javascript AST, made type-safe with typescript. Renders to javascript code with source maps. Used by Mason.
	
	\item \tit{dum} \enspace \small{build system} \hfill \textsf{2015-} \\
	Simple build system: translates files from e.g. jade to html, or coffeescript to javascript. No build script necessary. \\
	Instead of specialized plugins, uses jstransformers. Completely asynchronous. Written in Mason.

	\item \tit{painterly rendering} \enspace \small{webgl rendering experiment} \hfill \textsf{spring 2014} \\
	Team of 2. Real-time webgl, with HTML UI to modify renderer properties. \\
	Renders a 3D particle system of brush stroke sprites which orient and curve along edges of objects and around centers of light.

	\item \tit{logic online} \enspace \small{online logic practice} \hfill \textsf{spring 2014} \\
	Deduction language (shared by server and client) and exercises to learn it. Inference and equality rules are asserted or proved within the language. Exercises are stored as YAML files.

	\item \tit{polo jeans} \enspace \small{webgl 2D game engine} \hfill \textsf{fall 2013} \\
	Team of 4. Lead meetings; worked on architecture, buld system, and media; wrote GameObject scripting, including multiple inheritance.
	
	\item \tit{LEIA} \enspace \small{natural language dependency grammar parser} \hfill \textsf{fall 2013} \\
	Team of 6. A restaurant-recommending robot. Users write English sentences to ask for information about local food. \\
	Wrote text to dependency grammar part of pipeline. Wrote onomasticon and lexicon as JSON data.

	\item \tit{ghost control} \enspace \small{control systems research video game} \hfill \textsf{summer 2013} \\
	Worked for control systems researchers. \\
	Web game that tracks user and saves/loads ghost data from server.

	\item \tit{wahoo} \enspace \small{scala 2D game engine} \hfill \textsf{fall 2012} \hfill \\
	Features: dynamic lighting, loose quadtree collision detection, and type-based (via reflection), state-based GameObject scripting.

	\item \tit{games} \hfill \textsf{2009-2013} \\
	Web games and desktop-based games. One game in OpenGL, one in OGRE, both with PyGame. Unfinished game written with Wahoo.	
	\end{noindlist}

\end{resume}
\end{document}